---
title: "Exercises5(Ch3.7)"
author: "Nathan Workman"
date: "January 17, 2019"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.height = 6, fig.width = 12)
library(ggplot2)
```



3.8.1 Exercises


1. What is the problem with this plot? How could you improve it?

```{r echo = F}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```

There is an overlapping of data. TO fix use the position = jitter

```{r echo = F}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy), position = "jitter") + 
  geom_point(mapping = aes(),position = "jitter")
```



2. What parameters to geom_jitter() control the amount of jittering?

\begin{itemize}
      \item Height- Horizontal Jitter placement
      \item Width- Vertical Jitter placemnet
      \end{itemize}


3. Compare and contrast geom_jitter() with geom_count().
geom jitter() is used for two varaibles with a continuous x and y to where as geom count() uses a discrete x and discrete y.

4. What's the default position adjustment for geom_boxplot()? Create a visualisation of the mpg dataset that demonstrates it.
The default position adjustment for geom boxplot() is dodge2.

```{r echo = F}
ggplot(data = mpg, aes(x = drv, y = hwy)) +
  geom_boxplot()
```

